Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-10-03 analysis/paper/paper.qmd
"fig-" option doesn't work for other figure. The figure that Ben tried was already working except for showing "Figure. 1".

#| label: tcsa-raw-materials
#| fig-cap: Histograms of TCSA values by lithic raw material.
#| fig-width:   4.5
#| fig-height:  4

@@

1)  About half of all the stemmed points made out of shale.
2)  Acidic volcanic rocks tend to have skewed lower TCSA values.
3)  But overall, there is no clear pattern of different TCSA values by raw material.

>>>>

#| label: fig-tcsa-raw-materials
#| fig-cap: Histograms of TCSA values by lithic raw material.
#| fig-width:   4.5
#| fig-height:  4

@@

1)  About half of all the stemmed points made out of shale (@fig-tcsa-raw-materials).
2)  Acidic volcanic rocks tend to have skewed lower TCSA values.
3)  But overall, there is no clear pattern of different TCSA values by raw material.
